### 2018-06-09 express2018/part2.tex
DS
Add a top-level TeX file (main)
Added (candidate) title and abstract

\documentclass{eptcs} % required template (EPTCS) by EXPRESS/SOS 2018

%% Math symbol packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathrsfs}

\usepackage{stmaryrd}
\SetSymbolFont{stmry}{bold}{U}{stmry}{m}{n}
% \cupdot (the best one)
\newcommand{\cupdot}{\mathbin{\mathaccent\cdot\cup}}

\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{proposition}
\newtheorem{proposition}{Proposition}[section]

% HOL theorem embedding support
\usepackage{holindex}
\usepackage{alltt}
\include{tokens}

\usepackage[all,cmtip]{xy}

\begin{document}

@@

van Glabbek further gave a way to construct congruence relations from
any existing equivalence relations:
\begin{definition}
\label{def:precc}
Given an equivalence relation $\sim$, its (pre)congruence closure,
notated as $[\sim]$ is defined by
\begin{equation}
g\,[\sim]\, h \mbox{ iff } C[g] \sim C[h] \mbox{ for every semantic
  context } C[\cdot].
\end{equation}
\end{definition}
And it's simple to prove that, for any equivation relation $\sim$,
$[\sim]$ is the coarsest congruence finer than $\sim$.

@@

As we know weak bisimilarity ($\approx$) is not (real) congruence, as
it doesn't satisfy subsitutivity on direct sums (but if the CCS syntax
is non-standard, i.e. has only prefixed sums, $\approx$ is indeed a
congruence). The purpose is to find a coarsest congruence contained in
weak bisimilarity. (``coarsest'' means, any other congruence finer than it must be contained in it)
There're two ways to build a congruence from weak bisimilarity, one
way is the standard definition for observational congruence (rooted
weak bisimilarity) $\approx^c$ in CCS textbooks, but even it's proven to be a
congruence we don't know if it's coarsest one.  The other way is to
build a (pre)congruence closure (Def.\,\ref{def:precc}) directly upon
the original weak bisimilarity relation, we call the resulting
relation ``Weak bisimilarity congruence'' ($[\approx]$):
\begin{alltt}
\HOLConst{WEAK_CONGR} \HOLSymConst{=} \HOLConst{CC} \HOLConst{WEAK_EQUIV}
\HOLConst{CC} \HOLFreeVar{R} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{g} \HOLBoundVar{h}. \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{c}. \HOLConst{CONTEXT} \HOLBoundVar{c} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{c} \HOLBoundVar{g}) (\HOLBoundVar{c} \HOLBoundVar{h}))
\end{alltt}
It can be shown that any such (pre)congruence closure is automatically coarset.

@@

\end{document}

>>>>

@@

van Glabbek further gave a way to construct congruence relations from
any existing equivalence relations:
\begin{definition}
Given an equivalence relation $\sim$, its (pre)congruence closure,
notated as $[\sim]$ is defined by
\begin{equation}
g\,[\sim]\, h \mbox{ iff } C[g] \sim C[h] \mbox{ for every semantic
  context } C[\cdot].
\end{equation}
\end{definition}
And it's simple to prove that, for any equivation relation $\sim$,
$[\sim]$ is the coarsest congruence finer than $\sim$.

@@

As we know weak bisimilarity ($\approx$) is not (real) congruence, as
it doesn't satisfy subsitutivity on direct sums (but if the CCS syntax
is non-standard, i.e. has only prefixed sums, $\approx$ is indeed a
congruence). The purpose is to find a coarsest congruence contained in
weak bisimilarity. (``coarsest'' means, any other congruence finer than it must be contained in it)
There're two ways to build a congruence from weak bisimilarity, one
way is the standard definition for observational congruence (rooted
weak bisimilarity) $\approx^c$ in CCS textbooks, but even it's proven to be a
congruence we don't know if it's coarsest one.  The other way is to
build a (pre)congruence closure (Def ??) directly upon
the original weak bisimilarity relation, we call the resulting
relation ``Weak bisimilarity congruence'' ($[\approx]$):
\begin{alltt}
\HOLConst{WEAK_CONGR} \HOLSymConst{=} \HOLConst{CC} \HOLConst{WEAK_EQUIV}
\HOLConst{CC} \HOLFreeVar{R} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{g} \HOLBoundVar{h}. \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{c}. \HOLConst{CONTEXT} \HOLBoundVar{c} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{c} \HOLBoundVar{g}) (\HOLBoundVar{c} \HOLBoundVar{h}))
\end{alltt}
It can be shown that any such (pre)congruence closure is automatically coarset.

@@
